---
title: "Lab 02 - Plastic waste"
author: "Annie Somerville"
date: "02.01.2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
glimpse (plastic_waste)
view (plastic_waste)
```

## Exercises

### Exercise 1

Most countries fall in the range of 0-1 kg/person, but Trinidad and Tobago has the highest amount of plastic waste per capita at 3.6 kg/person.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```

### Exercise 2

Color and fill were defined in (aes) because continent is part of the source dataframe, thus it has to be included in (aes). Alpha is a characteristic of the plotting geom instead of aesthetic because alpha is not part of the source dataframe.

```{r plastic-waste-density}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent)) +
  geom_density()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.3)
```

### Exercise 3

```{r plastic-waste-boxplot}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_boxplot()
```

### Exercise 4

Boxplots and violin plots show means and distributions of plastic waste per capita. It's easier for me to see the individual points (or countries) within continents on the boxplot compared to the violin plot, and it's easier for me to see the frequency (via density) of values on the violin plot.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 5

I don't see a clear relationship between plastic waste per capita and mismanaged waste per capita - the relationship looks undefined.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 6

There do seem to be clear distinctions between continents with respect to the association between plastic waste per capita and mismanaged plastic waste per captia. For example, it appears that Africa has a strong positive linear association between the two (the slope is very steep), whereas Europe's positive linear association seems a bit weaker (the slope is less steep).

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap,
                     color = continent)) +
  geom_point()
```

### Exercise 7

It looks like total population and plastic waste per capita may have a stronger linear relationship compared to coastal population and plastic waste per capita.

```{r plastic-waste-population-total}
ggplot(data = plastic_waste, 
       mapping = aes(x = total_pop, 
                     y = plastic_waste_per_cap)) +
  geom_point()
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop, 
                     y = plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
